\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-18 paper/paper.tex
paper changes

The mapping of underwater structures is a prominent task in underwater robotics. But only a few papers deal with the actual algorithm which is used to guide the robot during its exploration and mapping. Moreover we could not find any previous work that deals with guidance algorithm for the mapping of a horizontal structure via an autonomous underwater robot.\\

One paper that deals with the actual guiding algorithm is \textit{A behavior-based architecture for autonomous underwater exploration} \cite{rosenblatt2002behavior}. There the authors are using a behavior-based control architecture to safely guide a robot through a reef. Their robot follows a rope on the sea floor by utilizing a camera to get optical input. The rope acts in their case as a tool for collision avoidance and path planning as it can be safely laid out by humans beforehand.\\

Another paper which deals with the actual guiding of the robot is \textit{3-D terrain covering and map building algorithm for an AUV} \cite{lee20093}. In this paper the authors deal with the guidance and mapping of the ocean floor where we have multiple island or underwater mountains around. There the approach is in essence to explore the whole search space by exploring iteratively a plane for each depth level.\\

>>>>

The mapping of underwater structures is a common task in underwater robotics. Yet, only a few papers deal with the actual algorithm of mapping structures which is used to guide the robot during its exploration. Therefore we could not find any previous work that deals with guidance algorithms for the mapping of a horizontal structure via an autonomous underwater robot.\\

One paper that deals with the actual guiding algorithm is \textit{A behavior-based architecture for autonomous underwater exploration} \cite{rosenblatt2002behavior}. There the authors use a behavior-based control architecture to safely guide a robot through a reef. Their robot follows a rope on the sea floor by utilizing a camera to get optical input. The rope acts as a tool for collision avoidance and path planning as it can be safely laid out by humans beforehand.\\

Another paper which deals with the actual guiding of the robot is \textit{3-D terrain covering and map building algorithm for an AUV} \cite{lee20093}. In this paper the authors deal with the guidance and mapping of the ocean floor where we have multiple islands or underwater mountains around. The approach they use is to explore the whole space by exploring iteratively a plane for each depth level.\\
